Parallel Monte Carlo Synthetic Acceleration Methods for Discrete Transport Problems

### 2013-09-04 doc/dissertation/presentation/defense.tex
adding corrections from practice talk

  \begin{algorithm}[H]
    \caption{Power Iteration MCSA Scheme}
    \label{alg:power_iteration}
    \begin{algorithmic}
      \STATE $k_0 =$ initial guess
      \STATE $\mathbf{\Phi}_0 =$ initial guess
      \STATE $n = 0$
      \WHILE{$|\frac{k^n - k^{n-1}}{k^n}| < \epsilon$}
      \STATE $\mathbf{M} \mathbf{\Phi}^{n+1} = \frac{1}{k^n} \mathbf{F} \mathbf{\Phi}^n$
      \COMMENT{Solve for the new flux state with MCSA}
      \STATE $k^{n+1} = k^n \frac{\int \mathbf{F} \mathbf{\Phi}^{n+1} d\mathbf{r}}{\int
        \mathbf{F} \mathbf{\Phi}^n d\mathbf{r}}$
      \STATE $n = n+1$
      \ENDWHILE
    \end{algorithmic}
  \end{algorithm}

@@

  \begin{itemize}
    {\small
    \item Drekar is a production CFD code using Newton methods with
      FAD
      \medskip
    \item MCLS incorporated into Drekar nonlinear scheme to implement
      FANM
      \medskip
    \item Newton-Krylov method with Aztec GMRES used for benchmark
      comparisons
    \item All problems preconditioned with explicit scheme using
      algebraic multigrid (ML) and leveraged some kind of
      globalization (e.g. backtracking) 
    }
  \end{itemize}

@@

      \small{
        \begin{itemize}
        \item Weaker preconditioning at Ra=\sn{1}{-5} case
          \medskip
        \item $\eta_k = \gamma \Big(
          \frac{||\ve{F}(\ve{u}_k)||}{||\ve{F}(\ve{u}_{k-1})||}
          \Big)^{\alpha}$
          \medskip
        \item Constant forcing term for Ra=\sn{1}{-6} case
          \medskip
        \item RDA applied in all cases
        \end{itemize}
      }

@@

  \let\thefootnote\relax\footnote{\tiny{Wagner et. al., "Hybrid and
      parallel domain-decomposition methods development to enable
      Monte Carlo for reactor analysis", Joint International
      Conference on Supercomputing in Nuclear Applications and Monte
      Carl (SNA+MC 2010), 2010.}}
\end{frame}

@@

  \begin{itemize}
  \item Overlap values selected based on average 'diffusion length' of
    a history in the system of 2.6 discrete states
    \bigskip
  \item Overlap eliminates communication in the Monte Carlo sequence
    but simply differs it to an overlapping tally vector reduction
  \end{itemize}

>>>>

  \begin{algorithm}[H]
    \caption{Power Iteration MCSA Scheme}
    \label{alg:power_iteration}
    \begin{algorithmic}
      \STATE $k_0 =$ initial guess
      \STATE $\mathbf{\Phi}_0 =$ initial guess
      \STATE $n = 0$
      \WHILE{$|\frac{k^n - k^{n-1}}{k^n}| > \epsilon$}
      \STATE $\mathbf{M} \mathbf{\Phi}^{n+1} = \frac{1}{k^n} \mathbf{F} \mathbf{\Phi}^n$
      \COMMENT{Solve for the new flux state with MCSA}
      \STATE $k^{n+1} = k^n \frac{\int \mathbf{F} \mathbf{\Phi}^{n+1} d\mathbf{r}}{\int
        \mathbf{F} \mathbf{\Phi}^n d\mathbf{r}}$
      \STATE $n = n+1$
      \ENDWHILE
    \end{algorithmic}
  \end{algorithm}

@@

  \begin{itemize}
    {\small
    \item Drekar is a production CFD code using Newton methods with
      FAD
      \medskip
    \item MCLS incorporated into Drekar nonlinear scheme to implement
      FANM
      \medskip
    \item Newton-Krylov method with Aztec GMRES used for benchmark
      comparisons
    \item All methods and problems preconditioned with explicit scheme
      using algebraic multigrid (ML) and leveraged some kind of
      globalization (e.g. backtracking) }
  \end{itemize}

@@

      \small{
        \begin{itemize}
        \item Weaker preconditioning at Ra=\sn{1}{5} case
          \medskip
        \item $\eta_k = \gamma \Big(
          \frac{||\ve{F}(\ve{u}_k)||}{||\ve{F}(\ve{u}_{k-1})||}
          \Big)^{\alpha}$
          \medskip
        \item Constant forcing term for Ra=\sn{1}{6} case
          \medskip
        \item RDA applied in all cases
        \end{itemize}
      }

@@

  \let\thefootnote\relax\footnote{\tiny{Wagner et. al., "Hybrid and
      parallel domain-decomposition methods development to enable
      Monte Carlo for reactor analysis", Joint International
      Conference on Supercomputing in Nuclear Applications and Monte
      Carlo (SNA+MC 2010), 2010.}}
\end{frame}

@@

  \begin{itemize}
  \item Overlap values selected based on average 'diffusion length' of
    a history in the system of 2.6 discrete states
    \bigskip
  \item Overlap eliminates communication in the Monte Carlo sequence
    but simply defers it to an overlapping tally vector reduction
  \end{itemize}
